Don't Mind the Gap: Bridging Network-wide Objectives and Device-level Configurations

### 2016-01-29 paper/compilation.tex
typo

How could such a policy be implemented in BGP? Suppose we set the local preference at router $C$ to prefer $D$ over $E$, and use the BGP MED attribute to influence $W$ to prefer $A$ over $B$. This might work as expected under normal conditions, however, if the A -- C link fails, then suddenly $C$ has made the wrong decision. Traffic will now follow the
$W \cdot B \cdot C \cdot D$ path, even though this was path was not specified by the policy. This is a violation of \emph{Soundness}: The distributed implementation has used a route not specified by the policy. To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used. This is a violation of \emph{Completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
We could solve the first problem by placing a filter at router $B$ to prevent using a path that goes through $D$, but we can not help with the second problem: $C$ has made the wrong choice.

@@

In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and enumerating all failures is intractable. We thus adopt a conservative analysis based on the observations above. The high-level idea is to order each PGIR node according to a \textit{can prefer} relation. For example, node $(C,3,2)$ can be preferred to node $(C,-,2)$, but not the other way around. Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures. Formally this means that $N_1$ can be preferred to $N_2$ when:
%
$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
%
where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
there is always a path to each each ending location whenever this is a path from $N_2$ restricted to $G_i$.

>>>>

How could such a policy be implemented in BGP? Suppose we set the local preference at router $C$ to prefer $D$ over $E$, and use the BGP MED attribute to influence $W$ to prefer $A$ over $B$. This might work as expected under normal conditions, however, if the A -- C link fails, then suddenly $C$ has made the wrong decision. Traffic will now follow the
$W \cdot B \cdot C \cdot D$ path, even though this path was not specified by the policy. This is a violation of \emph{soundness}: The distributed implementation has used a route not specified by the policy. To make matters worse, the second preference $W \cdot B \cdot C \cdot E$ is available in the network but not being used. This is a violation of \emph{completeness}: A path for the best possible route available exists in the network but is not being used by the distributed implementation.
We could solve the first problem by placing routes that go through $D$ at $B$, however, we can not fix the second problem---$C$ has made the wrong choice. In fact, this policy can not be implemented in BGP in a way that is policy compliant under all failures.

@@

In general, ensuring that an individual router's preferences respect the policy under all possible failures is hard, and enumerating all failures is intractable. We thus adopt a conservative analysis based on the observations above. The high-level idea is to order each PGIR node according to a \textit{can prefer} relation. For example, node $(C,3,2)$ can be preferred to node $(C,-,2)$, but not the other way around. Intuitively, a node $N_1$ can be preferred to another node $N_2$ when, for each preference $N_2$ might achieve, there is a better preference that $N_1$ will achieve regardless of failures. Formally this means that $N_1$ can be preferred to $N_2$ when:
%
$$\forall i, \exists j, j \leq i \wedge protect(G_j, N_1, G_i, N_2)$$
%
where \textit{protect} means that, from $N_1$ on the product graph restricted to nodes that can potentially achieve preference $j$ or better, 
there is always a path to each ending location whenever this is a path from $N_2$ restricted to $G_i$.
